A generalized definition of multidimensional item response theory parameters

### 2022-07-27 output/paper_draft/paper_M2PLM_parameters.Rmd
Terminology correction, due to the ambiguity in the use of "vector" both as a geometric vector and an algebraic vector (i.e. column matrix) of the coordinates of such vector in a vector space.

Consider a $`r N_DIMS`$-dimensional latent space $`r LATENT_SPACE`$,
defined by vector space $V$ and basis $`r LS_BASIS`$,
being $`r LS_BASIS_EQ`$ an arbitrary set of linearly independent vectors.
A respondent is represented in $`r LATENT_SPACE`$ by
coordinate vector $`r TRAIT_VECTOR`$, assumed to be multivariate normal:

>>>>

Consider a $`r N_DIMS`$-dimensional latent space $`r LATENT_SPACE`$,
defined by vector space $V$ and basis $`r LS_BASIS`$,
being $`r LS_BASIS_EQ`$ an arbitrary set of linearly independent vectors.
A respondent is represented by vector $`r TRAIT_VEC_IN_LS`$,
with coordinates $`r TRAIT_VECTOR`$ in $`r LATENT_SPACE`$,
which is assumed to be a multivariate normal random variable:
